PRFDN: Reparameterize and Prune Disentangled U-Net for Efficient Image Super-resolution

### 2023-04-04 NTIRE 2023 RTSR Paper/PaperForReview.tex
取标题
加作者

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Branchy parallelized U-net structure

Branching, finetune, reparameterized, pruning

paralleled 
branched

Pruning reparameterized super-resolution model}
%多路径

\author{Daheng Yin, Baijun Chen, Mengyang Liu\\
School of Computer Science and Engineering, Southeast University, Nanjing, China\\
{\tt\small \{yindaheng98, bjchen, myliu\}@seu.edu.cn}
}
\maketitle

>>>>

%%%%%%%%% TITLE - PLEASE UPDATE
\title{PRFDN: Reparameterize and Prune Disentangled U-Net for Efficient Image Super-resolution}
%多路径

\author{Daheng Yin, Baijun Chen, Mengyang Liu, Fang Dong\\
School of Computer Science and Engineering, Southeast University, Nanjing, China\\
{\tt\small \{yindaheng98, bjchen, myliu, fdong\}@seu.edu.cn}
}
\maketitle
